HTW Hybrid Models

### 2024-03-04 Analysis/e3_test.qmd
assess hybrid fits and partial re-render

```{r setup3b, include=FALSE}
source(here::here("Functions", "packages.R"))
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e3Sbjs <- testE3 |> group_by(id,condit) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

e3_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    ylab("Predicted Deviation") + xlab("Velocity Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) 
```

@@

>>>>

```{r setup3b, include=FALSE}
source(here::here("Functions", "packages.R"))
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)
e3Sbjs <- testE3 |> group_by(id,condit,bandOrder) |> summarise(n=n())
testE3Avg <- testE3 %>% group_by(id, condit, vb, bandInt,bandType,tOrder) %>%
  summarise(nHits=sum(dist==0),vx=mean(vx),dist=mean(dist),sdist=mean(sdist),n=n(),Percent_Hit=nHits/n)
```

@@

e3_distBMM |> emmeans( ~condit + bandInt, 
                       at = list(bandInt = c(100, 350, 600, 800, 1000, 1200))) |>
  gather_emmeans_draws() |>
  ggplot(aes(x = bandInt, y = .value, color = condit, fill = condit)) + 
  stat_dist_pointinterval() +
  stat_lineribbon(alpha = .25, size = 1, .width = c(.95)) +
    ylab("Predicted Deviation") + xlab("Velocity Band")+
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

@@

indvSlopes |> 
  left_join(e3Sbjs, by=c("id","condit")) |>
  ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
  labs(x="Estimated Slope", y="Participant")  + 
  facet_wrap(~bandOrder+condit) + 
  {
  ggplot(indvSlopes |> 
    left_join(e3Sbjs, by=c("id","condit")), 
    aes(x = SlopeInt, color = condit)) + 
    geom_density() + 
        facet_wrap(~bandOrder) +
    labs(x="Slope Coefficient",y="Density")  }

### 2024-03-04 Model/hybrid.qmd
assess hybrid fits and partial re-render

```{r}
#| fig-height: 16
#| fig-width: 14

@@

ind_fits_df |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5)

ind_fits_df |> ggplot(aes(x=condit,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(~Fit_Method)

ind_fits_df |> 
   filter(id %in% unique(ind_fits_df$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(ind_fits_df$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(ind_fits_df$id)[1:50], Fit_Method=="Test_Train") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
    group_by(id,run_name,condit,Fit_Method) |> 
  mutate(rank=rank(mean_error)) |> 
  filter(rank<n_int*.50) |>
   filter(id %in% unique(ind_fits_df$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

ind_fits_df |> 
  group_by(id,condit,Fit_Method) |>
  mutate(we_med=median(weight_exam),
         Best_Model=case_when(we_med>.5 ~"EXAM",we_med<.5 ~"ALM")) |>
  filter(Fit_Method=="Test") |>
  ungroup() |>
  mutate(id=reorder(id,we_med,decreasing = TRUE)) |>
  ggplot(aes(x=weight_exam,y=id,col=Best_Model)) + 
  geom_vline(xintercept = .5,linetype="dashed") +
  stat_pointinterval() + 
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  theme_minimal() +
  theme(legend.position="top")

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) +
  facet_wrap(~run_name)

@@

all_fits |> 
   filter(id %in% unique(ind_fits_df$id)[1:50], Fit_Method=="Test") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

@@

## E2
```{r}

# folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904","e2_hybrid_n_iter_100_ntry_100_3211")

@@

@@

## E3
```{r}

# folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946","e3_hybrid_n_iter_100_ntry_100_0545")

>>>>

```{r}
#| fig-height: 14
#| fig-width: 13

@@

{all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) } /{

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) +
  facet_wrap(~run_name)
    }

all_fits |> ggplot(aes(x=condit,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(~Fit_Method)

all_fits |> ggplot(aes(x=run_name,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(condit~Fit_Method)

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
    group_by(id,run_name,condit,Fit_Method) |> 
  mutate(rank=rank(mean_error)) |> 
  filter(rank<n_int*.50) |>
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
  group_by(id,condit,Fit_Method) |>
  mutate(we_med=median(weight_exam),
         Best_Model=case_when(we_med>.5 ~"EXAM",we_med<.5 ~"ALM")) |>
  filter(Fit_Method=="Test") |>
  ungroup() |>
  mutate(id=reorder(id,we_med,decreasing = TRUE)) |>
  ggplot(aes(x=weight_exam,y=id,col=Best_Model)) + 
  geom_vline(xintercept = .5,linetype="dashed") +
  stat_pointinterval() + 
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  theme_minimal() +
  theme(legend.position="top")

@@

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5)

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

@@

## E2
```{r}
#| fig-height: 13
#| fig-width: 12
#| 
# folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904","e2_hybrid_n_iter_100_ntry_100_3211")

@@

{all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) } /{

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) +
  facet_wrap(~run_name)
    }

all_fits |> ggplot(aes(x=condit,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(~Fit_Method)

all_fits |> ggplot(aes(x=run_name,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(condit~Fit_Method)

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

all_fits |> 
  group_by(id,condit,Fit_Method) |>
  mutate(we_med=median(weight_exam),
         Best_Model=case_when(we_med>.5 ~"EXAM",we_med<.5 ~"ALM")) |>
  filter(Fit_Method=="Test") |>
  ungroup() |>
  mutate(id=reorder(id,we_med,decreasing = TRUE)) |>
  ggplot(aes(x=weight_exam,y=id,col=Best_Model)) + 
  geom_vline(xintercept = .5,linetype="dashed") +
  stat_pointinterval() + 
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  theme_minimal() +
  theme(legend.position="top")
```

## E3
```{r}
#| fig-height: 13
#| fig-width: 12
# folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946","e3_hybrid_n_iter_100_ntry_100_0545")
testE3 <- readRDS(here("data/e3_08-04-23.rds")) |> filter(expMode2 == "Test") 
e3Sbjs <- testE3 |> group_by(id,condit,bandOrder) |> summarise(n=n())

all_fits <- map_df(folder_names, process_folder) |> 
  left_join(e3Sbjs,by=c("id","condit"))

{all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) } /{

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) +
  facet_wrap(~run_name)
    }

all_fits |> 
   filter(Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +geom_density(alpha=.5) + facet_wrap(~bandOrder)

all_fits |> ggplot(aes(x=condit,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(bandOrder~Fit_Method)

all_fits |> ggplot(aes(x=run_name,y=weight_exam,col=condit)) + stat_pointinterval() +
  facet_wrap(condit~Fit_Method)

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
    ggplot(aes(x=weight_exam,fill=condit)) +
  geom_density() +
  geom_vline(xintercept = .5,linetype="dashed") +
  ggh4x::facet_wrap2(~id+condit, scales="free_y")

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

all_fits |> 
   filter(id %in% unique(all_fits$id)[1:50], Fit_Method=="Test_Train") |>
  ggplot(aes(x=run_name,y=weight_exam,col=run_name)) + 
  stat_pointinterval(position=position_dodge(.5)) +
  ggh4x::facet_wrap2(~id+condit) + 
  theme(axis.text.x = element_blank())

{all_fits |> 
  group_by(id,condit,Fit_Method) |>
  mutate(we_med=median(weight_exam),
         Best_Model=case_when(we_med>.5 ~"EXAM",we_med<.5 ~"ALM")) |>
  filter(Fit_Method=="Test") |>
  ungroup() |>
  mutate(id=reorder(id,we_med,decreasing = TRUE)) |>
  ggplot(aes(x=weight_exam,y=id,col=Best_Model)) + 
  geom_vline(xintercept = .5,linetype="dashed") +
  stat_pointinterval() + 
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  theme_minimal() +
  theme(legend.position="top")} / 
  {all_fits |> 
  group_by(id,condit,Fit_Method,bandOrder) |>
  mutate(we_med=median(weight_exam),
         Best_Model=case_when(we_med>.5 ~"EXAM",we_med<.5 ~"ALM")) |>
  filter(Fit_Method=="Test") |>
  ungroup() |>
  mutate(id=reorder(id,we_med,decreasing = TRUE)) |>
  ggplot(aes(x=weight_exam,y=id,col=Best_Model)) + 
  geom_vline(xintercept = .5,linetype="dashed") +
  stat_pointinterval() + 
  ggh4x::facet_grid2(~bandOrder+condit,axes="all",scales="free_y", independent = "y")+
  theme_minimal() +
  theme(legend.position="top")}

@@
